Efficient implementation of penalized regression\\for genetic risk prediction

### 2018-09-24 paper/draft.tex
need results + read again
need results.zip

\abstract{
Polygenic Risk Scores (PRS) consist in combining the information across many single-nucleotide polymorphisms (SNPs) in a score reflecting the genetic risk of developing a disease. PRS might have a major impact on public health, possibly allowing for screening campaigns to identify high-genetic risk individuals for a given disease.  
The ``Clumping+Thresholding'' (C+T) approach, which is the most common method to derive PRS, uses only univariate genome-wide association studies (GWAS) summary statistics, which makes it fast and easy to use. 
However, previous work showed that jointly estimating SNP effects for computing PRS has the potential to significantly improve the predictive performance of PRS as compared to C+T.

@@

Finally, for the penalized logistic regression (PLR), we find regression coefficients $\beta_0$ and $\beta$ that minimize the following regularized loss function $$L(\lambda, \alpha) = \underbrace{ -\sum_{i=1}^n \left( y_i \log\left(p_i\right) + (1 - y_i) \log\left(1 - p_i\right) \right) }_\text{Loss function}   +   \underbrace{ \lambda \left((1-\alpha)\frac{1}{2}\|\beta\|_2^2 + \alpha \|\beta\|_1\right) }_\text{Penalization} ~,$$ where $p_i=1/\left(1+\exp\left(-(\beta_0 + x_i^T\beta)\right)\right)$, $x$ is denoting the genotypes and covariables (e.g.\ principal components), $y$ is the disease status to predict, $\lambda$ and $\alpha$ are two regularization hyper-parameters that need to be chosen.
Different regularizations can be used to prevent overfitting, among other benefits: the L2-regularization (``ridge'', \cite{hoerl1970ridge}) shrinks coefficients and is ideal if there are many predictors drawn from a Gaussian distribution (corresponds to $\alpha = 0$ in the previous equation);
the L1-regularization (``lasso'', \cite{tibshirani1996regression}) forces some of the coefficients to be equal to zero and can be used as a means of variable selection, leading to sparse models (corresponds to $\alpha = 1$);
the L1- and L2-regularization (``elastic-net'', \cite{zou2005regularization}) is a compromise between the two previous penalties and is particularly useful in the $p \gg n$ situation ($p$: number of SNPs), or any situation involving many correlated predictors (corresponds to $0 < \alpha < 1$) \cite[]{friedman2010regularization}. In this study, we use an embedded grid search over $\alpha \in \{1, 0.5, 0.05, 0.001\}$.

@@

To capture recessive and dominant effects on top of additive effects in PLR, we use simple feature engineering: we construct a separate dataset with 3 times as many variables as the initial one. 
For each SNP variable, we add two more variables coding for recessive and dominant effects: one variable is coded 1 if homozygous variant and 0 otherwise, and the other is coded 0 for homozygous referent and 1 otherwise.
We refer to this method as ``PLR3'' in the results.

@@

We compared penalized logistic regression (PLR) with the C+T method using whole-genome simulations of scenario \textnumero1 (Table \ref{tab:simus}).

@@

In practice, a particular value of the threshold of inclusion of SNPs should be chosen for the C+T method and this choice can dramatically impact the predictive performance of C+T. For example, in a model with only 30 causal SNPs, AUC ranges from less than 60\% when using all SNPs passing clumping to 90\% \emph{if} choosing the optimal p-value threshold (Figures \ref{fig:main-AUC-PRS} and \ref{fig:supp-AUC-PRS}).

@@

We tested the T-Trees method in scenario \textnumero1.
As compared to PLR, T-Trees perform worse in terms of predictive ability, while taking much longer to run and making more complex predictive models because T-Trees use more predictors and non-linear effects (Figure \ref{fig:supp-ttrees}). 
Even when simulating with model ``COMP'' in which there are dominant and interaction-type effects that T-Trees should be able to handle, AUC is still lower when using T-Trees than when using PLR (Figure \ref{fig:supp-ttrees}).

We also compared the two penalized logistic regressions in scenario \textnumero1, PLR and PLR3 that uses additional features (variables) coding for recessive and dominant effects.
Predictive performance of PLR3 are nearly as good as PLR when there are only addtive effects (differences of AUC are always smaller than 2\%) and can lead to significantly greater results when there are also dominant and interactions effects (Figures \ref{fig:supp-triple} and \ref{fig:supp-AUC-triple}). For model ``COMP'', PLR3 provides AUC values at least 3.5\% higher than PLR, excepted when there are 3000 causal SNPs.
Yet, PLR3 takes 2-3 times as much time to run and requires 3 times as much disk storage as PLR.

@@

First, when reproducing simulations of scenario \textnumero1 using chromosome 6 only (scenario \textnumero2), the predictive performance of PLR always increase (Figure \ref{fig:supp-AUC-chr6-all-r2}). 
There is particularly a large increase when simulating 3000 causal SNPs: AUC from PLR increases from 60\% to nearly 80\% for Gaussian effects and a disease heritability of 80\%.
On the contrary, when simulating only 30 or 300 causal SNPs with the corresponding dataset, AUC of ``C+T-max'' does not increase, and even decreases for an heritability of 80\% (Figure \ref{fig:supp-AUC-chr6-all-r2}). 
Secondly, when varying the training size (scenario \textnumero3), we report an increase of AUC with a larger training size, with a faster increase of AUC provided with PLR as compared to ``C+T-max'' (Figure  \ref{fig:main-AUC-ntrain}).

@@

In this comparative study, we present a computationally efficient implementation of penalized logistic regression (PLR). 
This model can be used to build polygenic risk scores based on very large individual-level SNP datasets such as the UK biobank \cite[]{bycroft2017genome}. 
In agreement with previous work \cite[]{abraham2013performance}, we show that jointly estimating SNP effects has the potential to substantially improve predictive performance as compared to the standard C+T approach in which SNP effects are learned independently. 
PLR nearly always outperform the C+T method, and the benefits of using PLR are more pronounced with an increasing sample size or when causal SNPs are correlated with one another.

@@

The choice of hyper-parameter values is very important since it can greatly impact method performance. In the C+T method, there are two main hyper-parameters: the $r^2$ and the $p_T$ thresholds that control how stringent are the clumping and thresholding steps, respectively. 
The choice of the $r^2$ threshold of the clumping step is important. 
Indeed, on the one hand, choosing a low value for this threshold may discard informative SNPs that are correlated.
Yet, on the other hand, when choosing a high value for this threshold, too much redundant information would be included in the model, which would add some noise to the PRS.
Based on the simulations, we find that using a stringent threshold ($r^2 = 0.05$) leads to higher predictive performance, even when causal SNPs are correlated. It means that, in most cases, avoiding redundant information is more important than including all causal SNPs.
The choice of the $p_T$ threshold is also very important as it can greatly impact the predictive performance of the C+T method, which we confirm in this study \cite[]{ware2017heterogeneity}. 
In this paper, we reported the maximum AUC of 102 different p-value thresholds, a threshold that should normally be learned on the training set only. To our knowledge, there is no clear standard on how to choose these two critical hyper-parameters.

On the contrary, in the penalized logistic regression presented here, we developed an automatic procedure called Cross-Model Selection and Averaging (CMSA) that releases investigators from the burden of choosing hyper-parameter $\lambda$ that accounts for the amount of regularization used in the model. Not only this procedure provides near-optimal results, but it also accelerates the model training thanks to the development of an early stopping criterion. 
Usually, cross-validation is used to choose hyper-parameter values and then the model is trained again with these particular hyper-parameter values \cite[]{Hastie2008,wei2013large}. Yet, performing cross-validation and retraining the model is computationally demanding; CMSA offers a less burdensome alternative. 
Concerning hyper-parameter $\alpha$ that accounts for the relative importance of the L1 and L2 regularizations, we use a grid  search directly embedded in the CMSA procedure. 
%Our penalized logistic regression implementation does not allow for setting $\alpha = 0$, a model that would assume the infinitesimal model. Yet, if using e.g.\ $\alpha = 0.001$, it would lead to a similar model.

@@

We also explored how to capture non-linear effects. For this, we introduced a simple feature engineering technique that enables PLR to detect and learn not only additive effects, but also dominant and recessive effects. 
This technique improves the predictive performance of PLR when there are some non-linear effects in the simulations, while providing nearly the same predictive performance when there are only additive effects. Moreover, it also improves predictive performance for the celiac disease.

Yet, this approach is not able to detect interaction-type effects. 
In order to capture interaction-type effects, we tested T-Trees, a method that is able to exploit SNP correlations thanks to special decision trees \cite[]{botta2014exploiting}. 
However, predictive performance of T-Trees were consistently lower than with penalized logistic regression, even when simulating a model with dominant and interaction-type effects that T-Trees should be able to handle.

@@

Our approach has one major limitation: the main advantage of the C+T method is its direct applicability to summary statistics, allowing to leverage the largest GWAS results to date, even when individual cohort data cannot be merged because of practical or ethical reasons (e.g.\ consortium data including many cohorts). As of today, the proposed penalized logistic regression does not allow for the analysis of summary data, but this represents an important future direction of our work. The current version is of particular interest for the analysis of modern SNP datasets including hundreds of thousands of individuals.

@@

In this comparative study, we have presented a computationally efficient implementation of penalized logistic regression that can be used to predict disease status based on genotypes. Note that a similar penalized linear regression is also available in our software. 
Usually, joint statistical learning methods are so computationally demanding that they cannot be used on large-scale datasets such as the UK biobank \cite[]{bycroft2017genome}. 
A partial solution to this problem is to pre-filter data, but it usually leads to a decrease in predictive performance as some information is removed \cite[]{accuheight2018}. This pre-filtering step is not necessary anymore thanks to our implementation.
Moreover, the model we present in this paper can flexibly adapt to traits with different architectures thanks to two hyper-parameters that are automatically learned with the model. Thus, we strongly believe that our implementation of penalized regressions would be appropriate for predicting autoimmune diseases with a few strong effects (e.g.\ celiac disease) as well as highly polygenic traits (e.g.\ standing height). These models could also be used to predict phenotypes based on other omics data since the implementation is not specific to genotype data.

@@

\subsection*{``Fancy'' model}

@@

We used three different ways to estimate the maximum achievable AUC for our simulations.
First, we used the estimation from equation (3) of \cite{wray2010genetic}. For a prevalence fixed at 30\% and an heritability of 50\% (respectively 80\%), the approximated theoretical values of AUC are 84.1\% (respectively 93.0\%). Note that this approximation is reported to be less accurate for high heritabilities.
Secondly, if we assume that the genetic part of the liabilities follows a Gaussian distribution $N(0, h^2)$ and that the environmental part follows a Gaussian distribution $N(0, 1 - h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the disease heritability $h^2$ through Monte Carlo simulations. We report AUCs of 84.1\% and 94.1\% for an heritability of 50\% and 80\%, respectively.
Thirdly, we reproduce the exact same procedure of simulations and, for each combination of parameters (Table \ref{tab:simus}), we estimate the AUC of the ``oracle'', i.e.\ the true simulated genetic part of the liabilities through 100 replicates. For every combination of parameters, AUC of oracles are comprised between 83.2\% and 84.2\% for an heritability of 50\% and between 93.2\% and 94.1\% for an heritability of 80\%.
Given all these estimates of the maximal achievable AUC and for the sake of simplicity, we report maximum AUCs of 84\% (94\%) for heritabilities of 50\% (80\%) whatever are the parameters of the simulations.

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-ttrees}}
\caption{Comparison of T-Trees and PLR in scenario \textnumero1 for an heritability of 80\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for the ``simple'' and ``fancy'' models for simulating phenotypes. \textbf{A:} Mean of AUC over 5 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. \textbf{B:} Boxplots of numbers of predictors used by the methods for 5 simulations. \textbf{C:} Boxplots of execution times for 5 simulations.}
\label{fig:supp-ttrees}
\end{figure}

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-triple}}
\caption{Comparison of PLR3 and PLR in scenario \textnumero1 for an heritability of 80\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for the ``simple'' and ``fancy'' models for simulating phenotypes. \textbf{A:} Mean of AUC over 100 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. \textbf{B:} Boxplots of numbers of predictors used by the methods for 100 simulations. \textbf{C:} Boxplots of execution times for 100 simulations.}
\label{fig:supp-triple}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-triple}}
\caption{Comparison of PLR3 and PLR in scenario \textnumero1 for an heritability of 50\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for the ``simple'' and ``fancy'' models for simulating phenotypes. \textbf{A:} Mean of AUC over 100 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:supp-AUC-triple}
\end{figure}

>>>>

\abstract{
Polygenic Risk Scores (PRS) consist in combining the information across many single-nucleotide polymorphisms (SNPs) in a score reflecting the genetic risk of developing a disease. PRS might have a major impact on public health, possibly allowing for screening campaigns to identify high-genetic risk individuals for a given disease.  
The ``Clumping+Thresholding'' (C+T) approach is the most common method to derive PRS. C+T uses only univariate genome-wide association studies (GWAS) summary statistics, which makes it fast and easy to use. 
However, previous work showed that jointly estimating SNP effects for computing PRS has the potential to significantly improve the predictive performance of PRS as compared to C+T.

@@

Finally, for penalized logistic regression (PLR), we find regression coefficients $\beta_0$ and $\beta$ that minimize the following regularized loss function $$L(\lambda, \alpha) = \underbrace{ -\sum_{i=1}^n \left( y_i \log\left(p_i\right) + (1 - y_i) \log\left(1 - p_i\right) \right) }_\text{Loss function}   +   \underbrace{ \lambda \left((1-\alpha)\frac{1}{2}\|\beta\|_2^2 + \alpha \|\beta\|_1\right) }_\text{Penalization} ~,$$ where $p_i=1/\left(1+\exp\left(-(\beta_0 + x_i^T\beta)\right)\right)$, $x$ is denoting the genotypes and covariables (e.g.\ principal components), $y$ is the disease status to predict, $\lambda$ and $\alpha$ are two regularization hyper-parameters that need to be chosen.
Different regularizations can be used to prevent overfitting, among other benefits: the L2-regularization (``ridge'', \cite{hoerl1970ridge}) shrinks coefficients and is ideal if there are many predictors drawn from a Gaussian distribution (corresponds to $\alpha = 0$ in the previous equation);
the L1-regularization (``lasso'', \cite{tibshirani1996regression}) forces some of the coefficients to be equal to zero and can be used as a means of variable selection, leading to sparse models (corresponds to $\alpha = 1$);
the L1- and L2-regularization (``elastic-net'', \cite{zou2005regularization}) is a compromise between the two previous penalties and is particularly useful in the $p \gg n$ situation ($p$ is the number of SNPs), or any situation involving many correlated predictors (corresponds to $0 < \alpha < 1$) \cite[]{friedman2010regularization}. In this study, we use an embedded grid search over $\alpha \in \{1,~0.5,~0.05,~0.001\}$.

@@

To capture recessive and dominant effects on top of additive effects in PLR, we use simple feature engineering: we construct a separate dataset with 3 times as many variables as the initial one. 
For each SNP variable, we add two more variables coding for recessive and dominant effects: one variable is coded 1 if homozygous variant and 0 otherwise, and the other is coded 0 for homozygous referent and 1 otherwise.
We refer to this method as ``PLR3'' in the rest of the paper.

@@

We compared penalized logistic regression (PLR) with the C+T method using simulations of scenario \textnumero1 (Table \ref{tab:simus}).

@@

In practice, a particular value of the threshold of inclusion of SNPs should be chosen for the C+T method and this choice can dramatically impact the predictive performance of C+T. 
For example, in a model with 30 causal SNPs only, AUC ranges from less than 60\% when using all SNPs passing clumping to 90\% \emph{if} choosing the optimal p-value threshold (Figures \ref{fig:main-AUC-PRS} and \ref{fig:supp-AUC-PRS}).

@@

We tested the T-Trees method in scenario \textnumero1.
As compared to PLR, T-Trees perform worse in terms of predictive ability, while taking much longer to run (Figure \ref{fig:supp-ttrees}). 
Even for simulations with model ``COMP'' in which there are dominant and interaction-type effects that T-Trees should be able to handle, AUC is still lower when using T-Trees than when using PLR (Figure \ref{fig:supp-ttrees}).

We also compared the two penalized logistic regressions in scenario \textnumero1: PLR versus PLR3 that uses additional features (variables) coding for recessive and dominant effects.
Predictive performance of PLR3 are nearly as good as PLR when there are only addtive effects (differences of AUC are always smaller than 2\%) and can lead to significantly greater results when there are also dominant and interactions effects (Figures \ref{fig:supp-triple} and \ref{fig:supp-AUC-triple}). For model ``COMP'', PLR3 provides AUC values at least 3.5\% higher than PLR, excepted when there are 3000 causal SNPs.
Yet, PLR3 takes 2-3 times as much time to run and requires 3 times as much disk storage as PLR.

@@

First, when reproducing simulations of scenario \textnumero1 using chromosome 6 only (scenario \textnumero2), the predictive performance of PLR always increase (Figure \ref{fig:supp-AUC-chr6-all-r2}). 
There is a particularly large increase when simulating 3000 causal SNPs: AUC from PLR increases from 60\% to nearly 80\% for Gaussian effects and a disease heritability of 80\%.
On the contrary, when simulating only 30 or 300 causal SNPs with the corresponding dataset, AUC of ``C+T-max'' does not increase, and even decreases for an heritability of 80\% (Figure \ref{fig:supp-AUC-chr6-all-r2}). 
Secondly, when varying the training size (scenario \textnumero3), we report an increase of AUC with a larger training size, with a faster increase of AUC for PLR as compared to ``C+T-max'' (Figure  \ref{fig:main-AUC-ntrain}).

@@

In this comparative study, we present a computationally efficient implementation of penalized logistic regression (PLR). 
This model can be used to build polygenic risk scores based on very large individual-level SNP datasets such as the UK biobank \cite[]{bycroft2017genome}. 
In agreement with previous work \cite[]{abraham2013performance}, we show that jointly estimating SNP effects has the potential to substantially improve predictive performance as compared to the standard C+T approach in which SNP effects are learned independently. 
PLR always outperform the C+T method, excepted in some highly underpowered cases, and the benefits of using PLR are more pronounced with an increasing sample size or when causal SNPs are correlated with one another.

@@

The choice of hyper-parameter values is very important since it can greatly impact method performance. In the C+T method, there are two main hyper-parameters: the $r^2$ and the $p_T$ thresholds that control how stringent are the clumping and thresholding steps, respectively. 
The choice of the $r^2$ threshold of the clumping step is important. 
Indeed, on the one hand, choosing a low value for this threshold may discard informative SNPs that are correlated.
Yet, on the other hand, when choosing a high value for this threshold, too much redundant information would be included in the model, which would add some noise to the PRS.
Based on the simulations, we find that using a stringent threshold ($r^2 = 0.05$) leads to higher predictive performance, even when causal SNPs are correlated. It means that, in most cases, avoiding redundant information is more important than including all causal SNPs.
The choice of the $p_T$ threshold is also very important as it can greatly impact the predictive performance of the C+T method, which we confirm in this study \cite[]{ware2017heterogeneity}. 
In this paper, we reported the maximum AUC of 102 different p-value thresholds, a threshold that should normally be learned on the training set only. To our knowledge, there is no clear standard on how to choose these two critical hyper-parameters for C+T.

On the contrary, for the penalized logistic regression presented here, we developed an automatic procedure called Cross-Model Selection and Averaging (CMSA) that releases investigators from the burden of choosing hyper-parameter $\lambda$ that accounts for the amount of regularization used in the model. Not only this procedure provides near-optimal results, but it also accelerates the model training thanks to the development of an early stopping criterion. 
Usually, cross-validation is used to choose hyper-parameter values and then the model is trained again with these particular hyper-parameter values \cite[]{Hastie2008,wei2013large}. Yet, performing cross-validation and retraining the model is computationally demanding; CMSA offers a less burdensome alternative. 
Concerning hyper-parameter $\alpha$ that accounts for the relative importance of the L1 and L2 regularizations, we use a grid  search directly embedded in the CMSA procedure. 
%Our penalized logistic regression implementation does not allow for setting $\alpha = 0$, a model that would assume the infinitesimal model. Yet, if using e.g.\ $\alpha = 0.001$, it would lead to a similar model.

@@

We also explored how to capture non-linear effects. For this, we introduced a simple feature engineering technique that enables PLR to detect and learn not only additive effects, but also dominant and recessive effects. 
This technique improves the predictive performance of PLR when there are some non-linear effects in the simulations, while providing nearly the same predictive performance when there are additive effects only. 
Moreover, it also improves predictive performance for the celiac disease.

Yet, this approach is not able to detect interaction-type effects. 
In order to capture interaction-type effects, we tested T-Trees, a method that is able to exploit SNP correlations and interactions thanks to special decision trees \cite[]{botta2014exploiting}. 
However, predictive performance of T-Trees were consistently lower than with penalized logistic regression, even when simulating a model with dominant and interaction-type effects that T-Trees should be able to handle.

@@

Our approach has one major limitation: the main advantage of the C+T method is its direct applicability to summary statistics, allowing to leverage the largest GWAS results to date, even when individual cohort data cannot be merged because of practical or ethical reasons (e.g.\ consortium data including many cohorts). As of today, the proposed penalized logistic regression does not allow for the analysis of summary data, but this represents an important future direction of our work. 
The current version is of particular interest for the analysis of modern individual-level datasets including hundreds of thousands of individuals.

@@

In this comparative study, we have presented a computationally efficient implementation of penalized logistic regression that can be used to predict disease status based on genotypes. Note that a similar penalized linear regression is also available in our software. 
Usually, joint statistical learning methods are so computationally demanding that they cannot be used on large-scale datasets such as the UK biobank \cite[]{bycroft2017genome}. 
A partial solution to this problem is to pre-filter data, but it usually leads to a decrease in predictive performance as some information is removed \cite[]{accuheight2018}. This pre-filtering step is not necessary anymore thanks to our implementation.
Moreover, the model we present in this paper can flexibly adapt to traits with different architectures thanks to two hyper-parameters that are automatically learned with the model. Thus, we strongly believe that our implementation of penalized regressions would be appropriate for predicting autoimmune diseases with a few strong effects (e.g.\ celiac disease) as well as highly polygenic traits (e.g.\ standing height). 
Finally, note that these models could also be used to predict phenotypes based on other omics data since the implementation is not specific to genotype data.

@@

\subsection*{Model ``COMP''}

@@

We used three different ways to estimate the maximum achievable AUC for our simulations.
First, we used the estimation from equation (3) of \cite{wray2010genetic}. For a prevalence fixed at 30\% and an heritability of 50\% (respectively 80\%), the approximated theoretical values of AUC are 84.1\% (respectively 93.0\%). Note that this approximation is reported to be less accurate for high heritabilities.
Secondly, if we assume that the genetic part of the liabilities follows a Gaussian distribution $N(0, h^2)$ and that the environmental part follows a Gaussian distribution $N(0, 1 - h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the disease heritability $h^2$ through Monte Carlo simulations. We report AUCs of 84.1\% and 94.1\% for an heritability of 50\% and 80\%, respectively.
Thirdly, we reproduce the exact same procedure of simulations and, for each combination of parameters (Table \ref{tab:simus}), we estimate the AUC of the ``oracle'', i.e.\ the true simulated genetic part of the liabilities through 100 replicates. For every combination of parameters, AUC of oracles are comprised between 83.2\% and 84.2\% for an heritability of 50\% and between 93.2\% and 94.1\% for an heritability of 80\%.
Given all these estimates of maximal achievable AUC and for the sake of simplicity, we report maximum AUCs of 84\% (94\%) for heritabilities of 50\% (80\%) whatever are the simulation parameters.

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-ttrees}}
\caption{Comparison of T-Trees and PLR in scenario \textnumero1 for an heritability of 80\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for models ``ADD'' and ``COMP'' for simulating phenotypes. \textbf{A:} Mean of AUC over 5 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. \textbf{B:} Boxplots of numbers of predictors used by the methods for 5 simulations. \textbf{C:} Boxplots of execution times for 5 simulations.}
\label{fig:supp-ttrees}
\end{figure}

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-triple}}
\caption{Comparison of PLR3 and PLR in scenario \textnumero1 for an heritability of 80\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for models ``ADD'' and ``COMP'' for simulating phenotypes. \textbf{A:} Mean of AUC over 100 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. \textbf{B:} Boxplots of numbers of predictors used by the methods for 100 simulations. \textbf{C:} Boxplots of execution times for 100 simulations.}
\label{fig:supp-triple}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-triple}}
\caption{Comparison of PLR3 and PLR in scenario \textnumero1 for an heritability of 50\%. Vertical panels are presenting results for effects following a Gaussian or Laplace distribution. Horizontal panels are presenting results for models ``ADD'' and ``COMP'' for simulating phenotypes. \textbf{A:} Mean of AUC over 100 simulations. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:supp-AUC-triple}
\end{figure}
